Simulation pipeline

### 2021-05-18 Analysis/02_Simulation_pipeline.Rmd
Update 02_Simulation_pipeline.Rmd

```{r}
## Loading the optimisation functions
source("../Functions/optim.replicate.R")
source("../Functions/optim.helpers.R")
```

```{r}
## Running the full optimisation
results <- optim.replicate(fun = simulate.facilitation(),
                           diagnose = var,
                           summarise = optim.summarise,
                           minimum = 20, maximum = 100,
                           stop.variance = 0.05,
                           verbose = TRUE,
                           bkp.path = "../Data/Processed/",
                           bkp.name = "sim_facilitation.rda")
```

>>>>

```{r}
## Loading the optimisation functions
source("../Functions/optim.replicate.R")
source("../Functions/optim.helpers.R")
source("../Functions/analyse.replicates.R")
```

You can then run this replicate function that will start by running 20 replicates (`mimimum`) and will increase the number of replicates by 5% until reaching 1000 replicates (`maximum`) or until the addition 5% increase does not increase the variance for each metric with each different level of removal by less than 5% (120 parameters!).

There are options to

```{r, eval = FALSE}
## Running the full optimisation
results <- optim.replicate(input.fun = simulate.facilitation,
                           diagnose = var,
                           summarise = optim.summarise,
                           minimum = 20, maximum = 1000,
                           stop.variance = 0.05,
                           verbose = TRUE,
                           bkp.path = "../Data/Processed/",
                           bkp.name = "sim_facilitation.rda")
```
> Note that you can use the parallel version by adding the argument `parallel = TRUE` that is automatised using the package `future` and `future.apply` which makes the whole process run on all your available cores but is way less verbose. Without using the parallel version, it takes roughly 10 hours (overnight) to run the analyses on an old 2.2Ghz 8GB core.

## Checking the results

We can then visualise the "convergence" of the results using the `analyse.replicate` function:

```{r}
## Check the change in variance for all 120 parameters
analyse.replicate("../Data/Processed/sim_facilitation.rda")
```
